\documentclass{letter}
\begin{document}
Vencislav Popov\\
University of Zurich\\
Zurich, Switzerland

\vspace{1pc}
\today\\

\vspace{1pc}
Dear Editorial Board, 

\vspace{6pt}
I wish to submit an original note entitled “A Vertical Partition of the Harmonic Series” for consideration by The American Mathematical Monthly. 

\vspace{6pt}
I confirm that this work is original and has not been published elsewhere, nor is it currently under consideration for publication elsewhere. Please note that an earlier Author's Original Manuscript preprint is available on arXiv. To preserve the integrity of your double-anonymous review process, the arXiv preprint utilizes a slightly different title ("A Triangular Column Decomposition of the Harmonic Series").

\vspace{6pt}
In this paper, I report on a structurally distinct, two-dimensional proof of the divergence of the harmonic series. This is significant because, while the classical literature is rich with elegant grouping arguments—most notably those utilizing horizontal blocks or triangular-number rows—this paper turns that geometry on its side. By arranging the natural numbers into a triangular array and summing down the columns, the harmonic series is partitioned into infinitely many convergent subseries.

\vspace{6pt}
I believe that this manuscript is appropriate for publication by The American Mathematical Monthly because it strongly aligns with the journal's goal of publishing clear, engaging mathematics that brings fresh perspectives to foundational topics. The aesthetic appeal of this vertical decomposition reveals a self-similar structure: each column yields a convergent reciprocal series with strictly convex denominators, yet the sequence of these column masses strictly dominates $2/k$. Thus, the harmonic series decomposes into convergent strands whose total masses are themselves asymptotically harmonic. 

\vspace{6pt}
I have no conflicts of interest to disclose. 

\vspace{6pt}
Please address all correspondence concerning this manuscript to me at vencislav.popov@gmail.com. Thank you for your consideration of this manuscript. 

\vspace{6pt}
Sincerely,

\vspace{6pt}
Ven Popov

\end{document}